### 2025-07-19 docs/article/Sections/results.tex
fix typo in results section, re-add graphs

Virtual Threads allocate a full call stack per thread, which is unmounted and
stored on the heap when suspended (e.g., during blocking I/O). In contrast,
Kotlin coroutines compile into state machines that capture only the minimal
execution state needed to resume computation. This typically allows coroutines
to scale more efficiently in terms of memory usage, especially under high
concurrency. These findings contrasts with prior research, such as Beronić et
al.~\cite{9803765}, which reported lower heap usage for Kotlin coroutines
(52--99~MB) compared to Java Virtual Threads (16--64~MB), albeit under
different workloads.

>>>>

Virtual Threads allocate a full call stack per thread, which is unmounted and
stored on the heap when suspended (e.g., during blocking I/O). In contrast,
Kotlin coroutines compile into state machines that capture only the minimal
execution state needed to resume computation. This typically allows coroutines
to scale more efficiently in terms of memory usage, especially under high
concurrency. These findings contrast with prior research, such as Beronić et
al.~\cite{9803765}, which reported lower heap usage for Java Virtual Threads (16--64~MB)
compared to Kotlin coroutines (52--99~MB), albeit under different workloads.
